---
title: "historicFires"
author: "Alex Chubaty"
date: "28 June 2022"
output:
  html_document:
    keep_md: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, results = "hold") ## TODO: use 'eval = TRUE'
```

# Overview

Creates raster layers of historic fires, which can be used with a wildfire simulator (*e.g.*, `fireSense` or `scfm`).

# Parameters

Provide a summary of user-visible parameters.

```{r moduleParams, echo = FALSE, eval = TRUE}
df_params <- SpaDES.core::moduleParams("historicFires", "..")
knitr::kable(df_params)
```

# Events

- `loadFires`: Loads the historic fire layer for the current simulation year.

# Data dependencies

## Input data

```{r moduleInputs, echo = FALSE, eval = TRUE}
df_inputs <- SpaDES.core::moduleInputs("historicFires", "..")
knitr::kable(df_inputs)
```

## Output data

```{r moduleOutputs, echo = FALSE, eval = TRUE}
df_outputs <- SpaDES.core::moduleOutputs("historicFires", "..")
knitr::kable(df_outputs)
```

# Links to other modules

Can be used with wildfire simulators (*e.g.*, `fireSense` or `scfm`) to simulate landscape disturbances.
